No Title

### 2017-10-26 paper/paper.tex
caption

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_mu.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for $\mu$ the absolute value of the dot product between the
vector connecting the main galaxies and the vector perpendicular to
the satellite plane.
In this case both the MW and M31 show a strong alignment.
Apparently this result is outside the expectations from the
simulations and atypical compared to the spherical results. 
However, this is not the case. The $\mu$ distributions in the
randomization and the simulation are consistent with a uniform
distribution.
Under such circumstances the result of $\mu\approx 1$ is as likely as
any other result.
\label{fig:scatter_mu}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{correlations_M31.pdf}
\includegraphics[width=1.0\textwidth]{correlations_MW.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_mu.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for $\mu$ the absolute value of the dot product between the
vector connecting the main galaxies and the vector perpendicular to
the satellite plane.
In this case both the MW and M31 show a strong alignment.
Apparently this result is outside the expectations from the
simulations and atypical compared to the spherical results. 
However, this is not the case. The $\mu$ distributions in the
randomization and the simulation are consistent with a uniform
distribution.
Under such circumstances $\mu\approx 1$ is as likely as
any other value.
\label{fig:scatter_mu}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{correlations_M31.pdf}
\includegraphics[width=1.0\textwidth]{correlations_MW.pdf}
\caption{Correlations between the normalized values for the plane
  width, $c/a$ ratio and $b/a$ ratio. 
The star corresponds to the LG, black circles with errorbars are the
results from simulations and the gray cloud is the resul from the
multivariate gaussian model.
Upper raw summarizes the results for M31 and the lower raw for the MW.
This simplified description allows us to quantify how atypical is the
LG compared to the simulation results. 
\label{fig:correlations}}
\end{figure*}
